### 2015-07-28 Harris_2015/manuscript-materials/draft.Rmd
stuff

\centering
$p(\vec{y}; \alpha, \beta) \propto exp(\sum_{i}\alpha_i y_i + \sum_{i\neq j}\beta_{ij}y_i y_j).$
\raggedright

@@

The fourth alternative method, described in @gotelli_empirical_2009, involved
simulating possible landscapes from a null model that retains the row and column
sums of the original matrix [@strong_ecological_1984]. Using the default options
in the Pairs software described in @gotelli_empirical_2009, I simulated the null
distribution of scaled C-scores (a test statistic describing the number of
*non*-co-occurrences between two species). The software then calculated a
$Z$ statistic for each species pair using this null distribution. After
multiplying this statistic by $-1$ so that positive values corresponded to
facilitation and negative values corresponded to competition, I used it as
another estimate of species interactions.

>>>>

\centering

$p(\vec{y}; \alpha, \beta) \propto exp(\sum_{i}\alpha_i y_i + \sum_{i\neq j}\beta_{ij}y_i y_j).$

\raggedright

@@

The fourth alternative method, described in @gotelli_empirical_2009, involved
simulating possible landscapes from a null model that retains the row and column
sums of the original matrix [@strong_ecological_1984]. Using the default options
in the Pairs software described in @gotelli_empirical_2009, I simulated the null
distribution of scaled C-scores (a test statistic describing the number of
*non*-co-occurrences between two species). The software then calculated a
$Z$ statistic for each species pair using this null distribution, which I used
as its estimator of species interactions.
